### 2021-04-26 evaluation.tex
Explain the difference between PAAR and CADE measurements
Resolves a comment from R2

We verified that the linear predicate precedence heuristic
trained in \cite{DBLP:conf/cade/Bartek020} outperforms the \texttt{frequency} heuristic.
Moreover, we confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.

>>>>

We confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
may outperform the ``simple'' linear predicate precedence heuristic
trained in \cite{DBLP:conf/cade/Bartek020}.\footnote{The measurements presented in \cref{tab:results}
are not directly comparable with those reported in \cite{DBLP:conf/cade/Bartek020}
due to differences in the validation problem sets and the computation environments.}
